Viral Sequence Sorting Tools Evaluation

### 2022-10-07 EnvironmentalData/DrinkingWaterMetagenomes/identifying_viral_contigs_environmental_dw.Rmd
Added figure to compare clusters of tools to dw script.

>>>>

myclusters_df <- tibble(combo=names(myclusters),
                            cluster_index=myclusters)

myclusters_df <- separate(myclusters_df, col=combo, into=c("CheckV", "DVF",
                                                            "Kaiju", "VIBRANT",
                                                            "VirSorter", "VirSorter2"),
                          sep=" ", remove = F)

tool_count <- as.data.frame(rbind(table(myclusters_df$CheckV, myclusters_df$cluster_index)[2,],
                          table(myclusters_df$DVF, myclusters_df$cluster_index)[2,],
                          table(myclusters_df$Kaiju, myclusters_df$cluster_index)[2,],
                          table(myclusters_df$VIBRANT, myclusters_df$cluster_index)[2,],
                          table(myclusters_df$VirSorter, myclusters_df$cluster_index)[2,],
                          table(myclusters_df$VirSorter2, myclusters_df$cluster_index)[2,])
                    )

tool_count$method <- c("CheckV", "DVF", "Kaiju", "VIBRANT", "VirSorter", "VirSorter2")

tool_count <- melt(tool_count)

colnames(tool_count) <- c("tool", "cluster_index", "tool_count")
```

```{r}
pal <- ggthemes::tableau_color_pal(palette="Tableau 10", type="regular")

ggplot(tool_count, aes(x=cluster_index, y=tool_count,
                   fill=cluster_index,
                   color=cluster_index)) +
  geom_bar(stat="identity") +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  scale_fill_manual(name="",
                     values = alpha(rev(pal(6)), 0.5)) +
  scale_color_manual(name="",
                     values = alpha(rev(pal(6)), 1)) +
  xlab("Cluster") +
  ylab("Number of Times in Cluster") + 
  facet_wrap(~tool, scales = "free")
```
